Meeting the Challenges of Modeling Astrophysical Thermonuclear Explosions: \castro, \maestro, and the \amrex\ Astrophysics Suite

### 2017-10-28 astronum_2017/astronum-amrex.tex
update plots

\begin{figure}[t]
\centering
\includegraphics[width=0.48\linewidth]{sedov_scaling}
\includegraphics[width=0.48\linewidth]{wdmerger_scaling}
\caption{\label{fig:castro-scaling} (left) \castro\ strong scaling on
  OLCF Titan for a pure hydro (Sedov w/ real EOS) problem.  The
  different colors represent different base resolutions.  We see
  excellent strong scaling for the single level runs.  For the
  $1024^3$ run, we also ran with one level of refinement by a factor
  of 2 (triangles) or a factor of 4 (squares), and see good strong
  scaling.  The variability (shown by the error bars) at high core
  counts shows we are becoming work-starved. (right) \castro\ strong
  scaling on OLCF Titan for a hydro + Poisson gravity (wdmerger)
  problem.  This problem uses a multipole solver to determine
  Dirichlet boundary conditions representing an isolated mass
  distribution, and then geometric multigrid to solve for the
  potential in the interior.  Two coarse grid sizes are shown, and
  demonstrate great strong scaling.  We also look at a single level of
  refinement (by a factor of 4) on top of this coarse grid.}
\end{figure}

@@

Figure~\ref{fig:castro-scaling} shows \castro\ scaling behavior for a
pure hydro problem with a real EOS and a hydro + self-gravity problem
with a real EOS.  All tests were run on OLCF Titan.  The AMD
processors in Titan can be used in an 8 or 16 cores / node
configuration.  For all these runs, we ran in the 16 cores / node
mode.  All runs also used the PGI 17.7 compilers.  We see excellent
scaling behavior for the pure hydro problem.  For the self-gravity
problem, we scale well with a uniform grid, but with a factor of 4
refinement for the AMR level on top of this, we observe degraded
performance at higher core counts.  This is a challenging problem, as
only 3\% of the domain volume is refined.  For a given core count,
there are a number of different combinations of MPI ranks and OpenMP
threads we can use.  In general, with multilevel problems, we found
the best performance with fewer MPI ranks and more OpenMP threads.

@@

\ack The work at Stony Brook was supported by DOE/Office of Nuclear
Physics grant DE-FG02-87ER40317 and NSF award AST-1211563.  The work
at LBNL was supported by the DOE Office of Advanced Scientific
Computing Research under Contract No, DE-AC02-05CH11231. An award of
computer time was provided by the Innovative and Novel Computational
Impact on Theory and Experiment (INCITE) program.  This research used
resources of the Oak Ridge Leadership Computing Facility at the Oak
Ridge National Laboratory, which is supported by the Office of Science
of the U.S. Department of Energy under Contract
No.\ DE-AC05-00OR22725.  We appreciate the efforts of the OLCF (and in
particular Fernanda Foertter) in organizing the GPU hackathons.  This
research used resources of the National Energy Research Scientific
Computing Center, which is supported by the Office of Science of the
U.S. Department of Energy under Contract No.\ DE-AC02-05CH11231.
The authors would like to thank Stony Brook Research Computing
and Cyberinfrastructure, and the Institute for Advanced Computational
Science at Stony Brook University for access to the high-performance
LIred and SeaWulf computing systems, the latter of which was made
possible by a \$1.4M National Science Foundation grant (\#1531492).
The GPU work benefited from a grant of an Titan X Pascal board
from NVIDIA Corporation through the GPU Grant Program.
Visualizations were done using \cite{yt}.  This research has
made use of NASA's Astrophysics Data System Bibliographic Services.

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.48\linewidth]{sedov_scaling}
\includegraphics[width=0.48\linewidth]{wdmerger_scaling}
\caption{\label{fig:castro-scaling} (left) \castro\ strong scaling on
  OLCF Titan for a pure hydro (Sedov w/ real EOS) problem.  The
  different colors represent different base resolutions.  We see
  excellent strong scaling for the single level runs.  For the
  $1024^3$ run, we also ran with one level of refinement by a factor
  of 2 (triangles) or a factor of 4 (squares), and see good strong
  scaling.  The variability (shown by the error bars) at high core
  counts shows we are becoming work-starved.  These runs used the PGI 17.7
  compilers.  (right) \castro\ strong
  scaling on OLCF Titan for a hydro + Poisson gravity (wdmerger)
  problem.  This problem uses a multipole solver to determine
  Dirichlet boundary conditions representing an isolated mass
  distribution, and then geometric multigrid to solve for the
  potential in the interior.  Two coarse grid sizes are shown, and
  demonstrate great strong scaling.  We also look at a single level of
  refinement (by a factor of 4) on top of this coarse grid.  These runs 
  used the Cray 8.5.7 compilers.}
\end{figure}

@@

Figure~\ref{fig:castro-scaling} shows \castro\ scaling behavior for a
pure hydro problem with a real EOS and a hydro + self-gravity problem
with a real EOS.  All tests were run on OLCF Titan.  The AMD
processors in Titan can be used in an 8 or 16 cores / node
configuration.  For all these runs, we ran in the 16 cores / node
mode.  We see excellent
scaling behavior for the pure hydro problem.  For the self-gravity
problem, we scale very well with a uniform grid, but with a factor of 4
refinement for the AMR level on top of this, we observe degraded
performance at higher core counts.  This is a challenging problem, as
only 3\% of the domain volume is refined.  For a given core count,
there are a number of different combinations of MPI ranks and OpenMP
threads we can use.  In general, with multilevel problems, we found
the best performance with fewer MPI ranks and more OpenMP threads.

@@

\ack The work at Stony Brook was supported by DOE/Office of Nuclear
Physics grant DE-FG02-87ER40317 and NSF award AST-1211563.  The work
at LBNL was supported by the DOE Office of Advanced Scientific
Computing Research under Contract No, DE-AC02-05CH11231. An award of
computer time was provided by the Innovative and Novel Computational
Impact on Theory and Experiment (INCITE) program.  This research used
resources of the Oak Ridge Leadership Computing Facility at the Oak
Ridge National Laboratory, which is supported by the Office of Science
of the U.S. Department of Energy under Contract
No.\ DE-AC05-00OR22725.  We appreciate the efforts of the OLCF (and in
particular Fernanda Foertter) in organizing the GPU hackathons.  This
research used resources of the National Energy Research Scientific
Computing Center, which is supported by the Office of Science of the
U.S. Department of Energy under Contract No.\ DE-AC02-05CH11231.
The authors would like to thank Stony Brook Research Computing
and Cyberinfrastructure, and the Institute for Advanced Computational
Science at Stony Brook University for access to the high-performance
LIred and SeaWulf computing systems, the latter of which was made
possible by a \$1.4M National Science Foundation grant (\#1531492).
The GPU work benefited from a grant of an Titan X Pascal board
from NVIDIA Corporation through the GPU Grant Program.
Visualizations were done using yt~\cite{yt}.  This research has
made use of NASA's Astrophysics Data System Bibliographic Services.
